---
title: "Lineup Checks Dashboard — PIP Data Revisions"
format: dashboard
server: shiny
theme: yeti
---

```{r}
#| context: setup
#| label: setup

library(data.table)
library(DT)

# Load source scripts
source(here::here("R", "process_data.R"))
source(here::here("R", "change_detection.R"))
source(here::here("R", "summary_tables.R"))

# Load both PPP years (suppress benign data.table shallow-copy warnings)
ppp_data_2021 <- suppressWarnings(
  process_ppp_data_extended("2021", data_dir = "data")
)
ppp_data_2017 <- suppressWarnings(
  process_ppp_data_extended("2017", data_dir = "data")
)

# Poverty lines differ by PPP version
poverty_lines_2021 <- c("3.0", "4.2", "8.3")
poverty_lines_2017 <- c("2.15", "3.65", "6.85")
```

# {.sidebar width="380px"}

## Data & Method Selection

### PPP Version
```{r}
shiny::radioButtons(
  "ppp_version",
  label = "PPP Version:",
  choices = c("2021" = "2021", "2017" = "2017"),
  selected = "2021"
)
```

### Significance Method
```{r}
shiny::selectInput(
  "method",
  label = "Change Detection Method:",
  choices = c(
    "Relative + Absolute Floor" = "relative",
    "Z-Score" = "zscore",
    "Absolute Difference" = "absolute"
  ),
  selected = "relative"
)
```

### Threshold
```{r}
shiny::sliderInput(
  "threshold",
  label = "Threshold:",
  min = 0,
  max = 10,
  value = 5,
  step = 0.1
)
```

### Absolute Floor (for Relative method)
```{r}
shiny::uiOutput("abs_floor_ui")
```

### Primary Indicators
```{r}
shiny::selectInput(
  "indicator",
  label = "Indicator:",
  choices = c("headcount", "mean"),
  selected = "headcount"
)
```

### Poverty Line
```{r}
shiny::selectInput(
  "poverty_line",
  label = "Poverty Line:",
  choices = poverty_lines_2021,
  selected = poverty_lines_2021[1L]
)
```

---

```{r}
#| context: server
#| label: server-core

# --- Core Reactives ---

# Reactive: current PPP dataset (full list)
merged_data <- reactive({
  if (input$ppp_version == "2021") {
    ppp_data_2021
  } else {
    ppp_data_2017
  }
})

# Reactive: threshold value (normalized to 0-1 scale for methods)
threshold_val <- reactive({
  switch(
    input$method,
    "relative" = input$threshold / 100,
    "zscore" = input$threshold,
    "absolute" = input$threshold / 100
  )
})

# Reactive: abs_floor (only used for relative method)
abs_floor_val <- reactive({
  if (input$method == "relative") {
    if (is.null(input$abs_floor)) 0.005 else input$abs_floor
  } else {
    0.005 # ignored for absolute/zscore methods
  }
})

# Reactive: dynamic year range bounds computed from actual data
year_range_bounds <- reactive({
  data <- merged_data()
  all_years <- c(
    data$agg_merged$reporting_year,
    data$lineups_merged$reporting_year
  )
  list(
    min = min(all_years, na.rm = TRUE),
    max = max(all_years, na.rm = TRUE)
  )
})

# Reactive: region-filtered aggregate data (shared across Aggregates page)
agg_region_filtered <- reactive({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)
  dt <- data$agg_merged[poverty_line == .pl]
  if (!is.null(input$year_range_agg)) {
    dt <- dt[
      reporting_year >= input$year_range_agg[[1L]] &
        reporting_year <= input$year_range_agg[[2L]]
    ]
  }
  if (!is.null(input$region_filter) && input$region_filter != "All") {
    dt <- dt[region_code == input$region_filter]
  }
  dt
})

# --- Dynamic UI outputs ---

# Update poverty line choices when PPP version changes
observeEvent(input$ppp_version, {
  pls <- if (input$ppp_version == "2021") {
    poverty_lines_2021
  } else {
    poverty_lines_2017
  }
  shiny::updateSelectInput(
    session,
    "poverty_line",
    choices = pls,
    selected = pls[1L]
  )
})

# Absolute floor slider (conditional on method)
output$abs_floor_ui <- shiny::renderUI({
  if (input$method == "relative") {
    shiny::sliderInput(
      "abs_floor",
      label = "Absolute Floor:",
      min = 0,
      max = 0.05,
      value = 0.005,
      step = 0.0001
    )
  }
})

# Year range sliders — bounds computed dynamically from actual data
output$year_range_agg_ui <- shiny::renderUI({
  bounds <- year_range_bounds()
  shiny::sliderInput(
    "year_range_agg",
    label = "Year Range:",
    min = bounds$min,
    max = bounds$max,
    value = c(bounds$min, bounds$max),
    step = 1L
  )
})

output$year_range_country_ui <- shiny::renderUI({
  bounds <- year_range_bounds()
  shiny::sliderInput(
    "year_range_country",
    label = "Year Range:",
    min = bounds$min,
    max = bounds$max,
    value = c(bounds$min, bounds$max),
    step = 1L
  )
})

# Country selector (populated from merged data)
country_choices <- reactive({
  data <- merged_data()
  sort(unique(data$lineups_merged$country_code))
})

output$country_selector_ui <- shiny::renderUI({
  shiny::selectInput(
    "country_filter",
    label = "Country:",
    choices = country_choices(),
    selected = country_choices()[1]
  )
})

# All-indicators selector (populated from merged data)
all_indicators_reactive <- reactive({
  data <- merged_data()
  unique_inds <- unique(c(
    data$survey_indicators,
    data$lineup_indicators,
    data$agg_indicators
  ))
  sort(unique_inds)
})

output$indicator_all_ui <- shiny::renderUI({
  shiny::selectInput(
    "indicator_all",
    label = "Indicator:",
    choices = all_indicators_reactive(),
    selected = "headcount"
  )
})

# --- Value boxes ---

output$flagged_agg <- shiny::renderUI({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  agg_data <- data$agg_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(agg_data),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  count <- sum(flagged[[paste0(input$indicator, "_flagged")]], na.rm = TRUE)
  total <- nrow(flagged)

  bslib::value_box(
    title = "Aggregates Flagged",
    value = count,
    subtitle = paste0("out of ", total),
    theme = if (count > 0) "warning" else "success",
    showcase = bsicons::bs_icon("exclamation-triangle")
  )
})

output$flagged_lineup <- shiny::renderUI({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  lineup_data <- data$lineups_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(lineup_data),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  count <- sum(flagged[[paste0(input$indicator, "_flagged")]], na.rm = TRUE)
  total <- nrow(flagged)

  bslib::value_box(
    title = "Lineup Flagged",
    value = count,
    subtitle = paste0("out of ", total),
    theme = if (count > 0) "warning" else "success",
    showcase = bsicons::bs_icon("exclamation-triangle")
  )
})

output$flagged_survey <- shiny::renderUI({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  survey_data <- data$surveys_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(survey_data),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  count <- sum(flagged[[paste0(input$indicator, "_flagged")]], na.rm = TRUE)
  total <- nrow(flagged)

  bslib::value_box(
    title = "Survey Flagged",
    value = count,
    subtitle = paste0("out of ", total),
    theme = if (count > 0) "warning" else "success",
    showcase = bsicons::bs_icon("exclamation-triangle")
  )
})

# ---- Tabular and plot outputs ----------------------------------------

# Change Overview: Regional Heatmap
output$tbl_heatmap <- DT::renderDT({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)
  dt <- build_overview_agg(
    data$agg_merged,
    indicator = input$indicator,
    poverty_line = .pl,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )
  DT::datatable(
    dt,
    filter = "top",
    rownames = FALSE,
    options = list(
      pageLength = 25L,
      # Default filter: show only flagged rows (flagged is the 7th column, index 6)
      searchCols = list(
        NULL,
        NULL,
        NULL,
        NULL,
        NULL,
        NULL,
        list(search = "true")
      )
    )
  )
})

# Change Overview: Flagged Lineup Changes
output$tbl_flagged_lineups <- shiny::renderTable(
  {
    shiny::req(input$poverty_line)
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    lineup_subset <- data$lineups_merged[poverty_line == .pl]
    flagged <- add_flag_col(
      data.table::copy(lineup_subset),
      input$indicator,
      method = input$method,
      threshold = threshold_val(),
      abs_floor = abs_floor_val()
    )

    flag_col_name <- paste0(input$indicator, "_flagged")
    ind_x <- paste0(input$indicator, ".x")
    ind_y <- paste0(input$indicator, ".y")
    ind_diff <- paste0(input$indicator, "_diff")

    flagged_subset <- flagged[
      get(flag_col_name) == TRUE,
      list(
        country_code,
        region_code = region_code.x,
        reporting_year,
        old_value = get(ind_y),
        new_value = get(ind_x),
        difference = get(ind_diff)
      )
    ]
    flagged_subset[, .sort_key := abs(difference)]
    data.table::setorder(flagged_subset, -.sort_key)
    flagged_subset[, .sort_key := NULL]
    flagged_subset
  },
  striped = TRUE,
  hover = TRUE,
  bordered = TRUE
)

# Aggregates: Time Series
output$plot_agg_ts <- shiny::renderPlot(
  {
    agg_data <- agg_region_filtered()

    if (nrow(agg_data) == 0L) {
      return(
        ggplot2::ggplot() +
          ggplot2::annotate(
            "text",
            x = 0.5,
            y = 0.5,
            label = "No data for selection"
          ) +
          ggplot2::theme_void()
      )
    }

    ind_x <- paste0(input$indicator, ".x")
    ind_y <- paste0(input$indicator, ".y")

    ggplot2::ggplot(agg_data, ggplot2::aes(x = reporting_year)) +
      ggplot2::geom_line(
        ggplot2::aes(y = .data[[ind_x]], color = "New"),
        linewidth = 1
      ) +
      ggplot2::geom_line(
        ggplot2::aes(y = .data[[ind_y]], color = "Old"),
        linewidth = 1,
        linetype = "dashed"
      ) +
      ggplot2::facet_wrap(~region_code) +
      ggplot2::scale_color_manual(
        values = c("New" = "#2E86AB", "Old" = "#A23B72")
      ) +
      ggplot2::labs(
        title = paste0(input$indicator, " Over Time"),
        x = "Year",
        y = input$indicator,
        color = "Version"
      ) +
      ggplot2::theme_minimal() +
      ggplot2::theme(
        legend.position = "top",
        panel.spacing = ggplot2::unit(1, "lines")
      )
  },
  height = 500
)

# Aggregates: Driver Table
output$tbl_driver <- shiny::renderTable(
  {
    shiny::req(input$poverty_line)
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    .region <- if (
      !is.null(input$region_filter) && input$region_filter != "All"
    ) {
      input$region_filter
    } else {
      "WLD"
    }

    .yr_max <- if (!is.null(input$year_range_agg)) {
      input$year_range_agg[[2L]]
    } else {
      max(data$lineups_merged[poverty_line == .pl]$reporting_year, na.rm = TRUE)
    }

    tryCatch(
      build_driver_table(
        data$lineups_merged,
        region = .region,
        year = .yr_max,
        poverty_line = .pl,
        indicator = input$indicator
      ),
      error = function(e) data.frame(Message = conditionMessage(e))
    )
  },
  striped = TRUE,
  hover = TRUE,
  bordered = TRUE
)

# Aggregates: Regional Comparison Bar Chart
output$plot_agg_bars <- shiny::renderPlot(
  {
    shiny::req(input$poverty_line)
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    agg_data <- data$agg_merged[poverty_line == .pl]
    latest_year <- max(agg_data$reporting_year, na.rm = TRUE)
    agg_latest <- agg_data[reporting_year == latest_year]

    ind_x <- paste0(input$indicator, ".x")
    ind_y <- paste0(input$indicator, ".y")
    agg_latest[, diff := get(ind_x) - get(ind_y)]

    ggplot2::ggplot(
      agg_latest,
      ggplot2::aes(x = reorder(region_code, -abs(diff)), y = diff)
    ) +
      ggplot2::geom_col(ggplot2::aes(fill = diff > 0), width = 0.7) +
      ggplot2::scale_fill_manual(
        values = c("TRUE" = "#06A77D", "FALSE" = "#D62828"),
        labels = c("TRUE" = "Increase", "FALSE" = "Decrease")
      ) +
      ggplot2::coord_flip() +
      ggplot2::labs(
        title = paste0(
          input$indicator,
          " Change by Region (",
          latest_year,
          ")"
        ),
        x = "Region",
        y = paste0("Change in ", input$indicator),
        fill = "Direction"
      ) +
      ggplot2::theme_minimal() +
      ggplot2::theme(legend.position = "top")
  },
  height = 400
)

# Country: Lineup Time Series
output$plot_country_ts <- shiny::renderPlot(
  {
    shiny::req(
      input$poverty_line,
      input$country_filter,
      input$year_range_country
    )
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    lineup_data <- data$lineups_merged[
      country_code == input$country_filter &
        poverty_line == .pl &
        reporting_year >= input$year_range_country[1] &
        reporting_year <= input$year_range_country[2]
    ]

    if (nrow(lineup_data) == 0) {
      return(
        ggplot2::ggplot() +
          ggplot2::annotate(
            "text",
            x = 0.5,
            y = 0.5,
            label = "No data available"
          ) +
          ggplot2::theme_void()
      )
    }

    ind_x <- paste0(input$indicator, ".x")
    ind_y <- paste0(input$indicator, ".y")

    plot_data <- lineup_data[, list(
      reporting_year,
      new_val = get(ind_x),
      old_val = get(ind_y)
    )]
    plot_data <- data.table::melt(
      plot_data,
      id.vars = "reporting_year",
      variable.name = "version",
      value.name = "value"
    )
    plot_data[, version := ifelse(version == "new_val", "New", "Old")]

    ggplot2::ggplot(
      plot_data,
      ggplot2::aes(
        x = reporting_year,
        y = value,
        color = version,
        linetype = version
      )
    ) +
      ggplot2::geom_line(linewidth = 1) +
      ggplot2::geom_point(size = 2) +
      ggplot2::scale_color_manual(
        values = c("New" = "#2E86AB", "Old" = "#A23B72")
      ) +
      ggplot2::scale_linetype_manual(
        values = c("New" = "solid", "Old" = "dashed")
      ) +
      ggplot2::labs(
        title = paste0(input$indicator, " \u2014 ", input$country_filter),
        x = "Year",
        y = input$indicator,
        color = "Version",
        linetype = "Version"
      ) +
      ggplot2::theme_minimal() +
      ggplot2::theme(legend.position = "top")
  },
  height = 400
)

# Country: Survey Data Comparison
output$tbl_survey <- shiny::renderTable(
  {
    shiny::req(
      input$poverty_line,
      input$country_filter,
      input$year_range_country
    )
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    survey_data <- data$surveys_merged[
      country_code == input$country_filter &
        poverty_line == .pl &
        reporting_year >= input$year_range_country[1] &
        reporting_year <= input$year_range_country[2]
    ]

    if (nrow(survey_data) == 0) {
      return(data.frame(Message = "No survey data available"))
    }

    ind_x <- paste0(input$indicator, ".x")
    ind_y <- paste0(input$indicator, ".y")
    ind_diff <- paste0(input$indicator, "_diff")

    result <- survey_data[, list(
      reporting_year,
      survey_year,
      old_value = get(ind_y),
      new_value = get(ind_x),
      difference = get(ind_diff)
    )]
    data.table::setorder(result, -reporting_year)
    result
  },
  striped = TRUE,
  hover = TRUE,
  bordered = TRUE
)

# Country: Source of Change
output$tbl_source <- shiny::renderTable(
  {
    shiny::req(
      input$poverty_line,
      input$country_filter,
      input$year_range_country
    )
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    source_tbl <- build_source_table(
      data$lineups_merged,
      country = input$country_filter,
      poverty_line = .pl,
      year_range = input$year_range_country
    )

    if (nrow(source_tbl) == 0) {
      return(data.frame(Message = "No explanatory variable data"))
    }
    source_tbl
  },
  striped = TRUE,
  hover = TRUE,
  bordered = TRUE
)

# Country: Survey Coverage Changes
output$tbl_coverage <- shiny::renderTable(
  {
    shiny::req(input$country_filter)
    data <- merged_data()

    survey_cov <- data$survey_coverage_diff[
      country_code == input$country_filter
    ]

    if (nrow(survey_cov) == 0) {
      return(data.frame(Message = "No survey coverage changes"))
    }

    survey_cov[, list(reporting_year, reporting_level, welfare_type, change)]
  },
  striped = TRUE,
  hover = TRUE,
  bordered = TRUE
)

# All Indicators: Scatter Plot
output$plot_scatter <- shiny::renderPlot(
  {
    shiny::req(input$poverty_line, input$indicator_all)
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    ind_x <- paste0(input$indicator_all, ".x")
    ind_y <- paste0(input$indicator_all, ".y")

    scatter_data <- data$lineups_merged[
      poverty_line == .pl &
        !is.na(get(ind_x)) &
        !is.na(get(ind_y))
    ]

    if (nrow(scatter_data) == 0) {
      return(
        ggplot2::ggplot() +
          ggplot2::annotate(
            "text",
            x = 0.5,
            y = 0.5,
            label = "No data available"
          ) +
          ggplot2::theme_void()
      )
    }

    ggplot2::ggplot(
      scatter_data,
      ggplot2::aes(
        x = .data[[ind_y]],
        y = .data[[ind_x]],
        color = region_code.x
      )
    ) +
      ggplot2::geom_point(size = 2, alpha = 0.7) +
      ggplot2::geom_abline(
        slope = 1,
        intercept = 0,
        linetype = "dashed",
        color = "gray50"
      ) +
      ggplot2::scale_color_viridis_d() +
      ggplot2::labs(
        title = paste0(input$indicator_all, " \u2014 Old vs New"),
        x = paste0(input$indicator_all, " (Old)"),
        y = paste0(input$indicator_all, " (New)"),
        color = "Region"
      ) +
      ggplot2::theme_minimal() +
      ggplot2::theme(legend.position = "right")
  },
  height = 500
)

# All Indicators: Bland-Altman Plot
output$plot_ba <- shiny::renderPlot(
  {
    shiny::req(input$poverty_line, input$indicator_all)
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    ind_x <- paste0(input$indicator_all, ".x")
    ind_y <- paste0(input$indicator_all, ".y")

    ba_data <- data$lineups_merged[
      poverty_line == .pl &
        !is.na(get(ind_x)) &
        !is.na(get(ind_y))
    ]

    if (nrow(ba_data) == 0) {
      return(
        ggplot2::ggplot() +
          ggplot2::annotate(
            "text",
            x = 0.5,
            y = 0.5,
            label = "No data available"
          ) +
          ggplot2::theme_void()
      )
    }

    ba_data[, mean_val := (get(ind_x) + get(ind_y)) / 2]
    ba_data[, diff_val := get(ind_x) - get(ind_y)]

    mean_diff <- mean(ba_data$diff_val, na.rm = TRUE)
    sd_diff <- sd(ba_data$diff_val, na.rm = TRUE)
    upper_loa <- mean_diff + 1.96 * sd_diff
    lower_loa <- mean_diff - 1.96 * sd_diff

    ggplot2::ggplot(
      ba_data,
      ggplot2::aes(x = mean_val, y = diff_val, color = region_code.x)
    ) +
      ggplot2::geom_point(size = 2, alpha = 0.7) +
      ggplot2::geom_hline(
        yintercept = mean_diff,
        linetype = "solid",
        color = "blue"
      ) +
      ggplot2::geom_hline(
        yintercept = upper_loa,
        linetype = "dashed",
        color = "red"
      ) +
      ggplot2::geom_hline(
        yintercept = lower_loa,
        linetype = "dashed",
        color = "red"
      ) +
      ggplot2::scale_color_viridis_d() +
      ggplot2::labs(
        title = paste0(input$indicator_all, " \u2014 Bland-Altman Plot"),
        x = paste0("Mean (", input$indicator_all, ")"),
        y = "Difference (New - Old)",
        color = "Region"
      ) +
      ggplot2::theme_minimal() +
      ggplot2::theme(legend.position = "right")
  },
  height = 500
)

# All Indicators: Flagged Outliers
output$tbl_outliers <- shiny::renderTable(
  {
    shiny::req(input$poverty_line, input$indicator_all)
    data <- merged_data()
    .pl <- as.numeric(input$poverty_line)

    outlier_data <- data$lineups_merged[poverty_line == .pl]
    outlier_flagged <- add_flag_col(
      data.table::copy(outlier_data),
      input$indicator_all,
      method = input$method,
      threshold = threshold_val(),
      abs_floor = abs_floor_val()
    )

    flag_col_name <- paste0(input$indicator_all, "_flagged")
    ind_x <- paste0(input$indicator_all, ".x")
    ind_y <- paste0(input$indicator_all, ".y")
    ind_diff <- paste0(input$indicator_all, "_diff")

    outliers <- outlier_flagged[
      get(flag_col_name) == TRUE,
      list(
        country_code,
        region_code = region_code.x,
        reporting_year,
        old_value = get(ind_y),
        new_value = get(ind_x),
        difference = get(ind_diff)
      )
    ]

    if (nrow(outliers) == 0) {
      return(data.frame(Message = "No flagged outliers"))
    }
    outliers[, .sort_key := abs(difference)]
    data.table::setorder(outliers, -.sort_key)
    outliers[, .sort_key := NULL]
    outliers
  },
  striped = TRUE,
  hover = TRUE,
  bordered = TRUE
)
```

# Change Overview

## Summary Statistics

### Aggregates
```{r}
shiny::uiOutput("flagged_agg")
```

### Lineup
```{r}
shiny::uiOutput("flagged_lineup")
```

### Survey
```{r}
shiny::uiOutput("flagged_survey")
```

## Regional Heatmap

```{r}
DT::DTOutput("tbl_heatmap")
```

## Flagged Changes by Country & Year

```{r}
tableOutput("tbl_flagged_lineups")
```

# Aggregates Detail

## {.sidebar}

```{r}
#| label: sidebar-aggregates-region
shiny::selectInput(
  "region_filter",
  label = "Region(s):",
  choices = c(
    "All",
    "AFE",
    "AFW",
    "EAS",
    "ECS",
    "LAC",
    "MNA",
    "SAR",
    "SSA",
    "WLD"
  ),
  selected = "All",
  multiple = FALSE
)

shiny::uiOutput("year_range_agg_ui")
```

## Time Series

```{r}
#| label: plot-agg-timeseries
plotOutput("plot_agg_ts", height = "500px")
```

## Driver Table

```{r}
#| label: table-driver
tableOutput("tbl_driver")
```

## Regional Comparison

```{r}
plotOutput("plot_agg_bars", height = "400px")
```

# Country Detail

## {.sidebar}

```{r}
#| label: sidebar-country
shiny::uiOutput("country_selector_ui")

shiny::uiOutput("year_range_country_ui")
```

## Lineup Time Series

```{r}
plotOutput("plot_country_ts", height = "400px")
```

## Survey Data Comparison

```{r}
tableOutput("tbl_survey")
```

## Source of Change

```{r}
tableOutput("tbl_source")
```

## Survey Coverage Changes

```{r}
tableOutput("tbl_coverage")
```

# All Indicators

## {.sidebar}

```{r}
shiny::uiOutput("indicator_all_ui")
```

## Scatter Plot (Old vs New)

```{r}
#| label: plot-scatter
plotOutput("plot_scatter", height = "500px")
```

## Bland-Altman Plot

```{r}
plotOutput("plot_ba", height = "500px")
```

## Flagged Outliers

```{r}
tableOutput("tbl_outliers")
```

# About

## How This Dashboard Works

This dashboard compares **new** PIP pipeline data against **old** (published)
data to identify meaningful changes in poverty estimates. It works across three
levels: regional/global **aggregates**, country-level **lineup years**
(interpolated/extrapolated), and **survey years** (actual survey data).

### Sidebar Controls

| Control | Description |
|---|---|
| **PPP Version** | Toggle between PPP 2021 (poverty lines: \$3.0, \$4.2, \$8.3/day) and PPP 2017 (\$2.15, \$3.65, \$6.85/day). |
| **Change Detection Method** | How changes are assessed for significance. See below. |
| **Threshold** | Sensitivity of the flagging. Lower = more flags. |
| **Absolute Floor** | Minimum absolute change required (Relative method only). Prevents flagging tiny values with large percentage swings. |
| **Indicator** | Primary poverty indicator to analyse (headcount or mean on main pages; all indicators on the "All Indicators" page). |
| **Poverty Line** | International poverty line in \$/day (PPP). Values update automatically with PPP version. |

### Change Detection Methods

**Relative + Absolute Floor** *(default)*

A change is flagged when **both** conditions are met:

- The relative change exceeds the threshold: $\frac{|\text{new} - \text{old}|}{|\text{old}|} > \frac{\text{threshold}}{100}$
- The absolute change exceeds the floor: $|\text{new} - \text{old}| > \text{abs\_floor}$

The absolute floor prevents false positives from near-zero values (e.g., a
headcount moving from 0.001 to 0.002 is a 100% relative change but
meaningless in practice).

**Z-Score**

Computes the z-score of each change relative to the distribution of all
changes (trimmed at 1% tails). A change is flagged when $|z| > \text{threshold}$.
Useful for detecting outliers in the distribution of revisions.

**Absolute Difference**

Flags changes where $|\text{new} - \text{old}| > \frac{\text{threshold}}{100}$.
Simplest method — treats all changes the same regardless of the baseline level.

### Pages

| Page | Purpose |
|---|---|
| **Change Overview** | Entry point. Value boxes show total flagged changes at each level. Regional heatmap and flagged-country table give a quick picture of where revisions occurred. |
| **Aggregates Detail** | Drill into regional aggregates. Time-series of old vs new, driver table showing which countries contribute most to a regional change, and a bar chart of change direction by region. |
| **Country Detail** | Select a country to see its lineup time-series, survey-year comparison, and a source-of-change panel showing which explanatory variables (GDP, consumption, population, CPI, welfare type) also changed. |
| **All Indicators** | Compare any indicator (not just headcount/mean). Scatter plot (old vs new with 45° line), Bland-Altman plot (agreement analysis), and an outlier table. |

### Interpreting the Threshold Slider

The slider ranges from 0 to 10. Its meaning depends on the method:

- **Relative**: Threshold 5 = flag changes > 5% relative difference
- **Z-Score**: Threshold 2 = flag changes > 2 standard deviations
- **Absolute**: Threshold 1 = flag changes > 0.01 in absolute terms

Setting the threshold to 0 shows **all** changes (nothing is filtered). This
ensures no revision is hidden — useful for a complete audit.
