---
title: "Lineup Checks Dashboard — PIP Data Revisions"
format: dashboard
server: shiny
theme: yeti
---

```{r}
#| context: setup
#| label: setup

library(data.table)
library(DT)
library(plotly)
library(bslib)
library(bsicons)

# Load source scripts
source(here::here("R", "process_data.R"))
source(here::here("R", "change_detection.R"))
source(here::here("R", "summary_tables.R"))

# Load both PPP years (suppress benign data.table shallow-copy warnings)
ppp_data_2021 <- suppressWarnings(
  process_ppp_data_extended("2021", data_dir = "data")
)
ppp_data_2017 <- suppressWarnings(
  process_ppp_data_extended("2017", data_dir = "data")
)

# Poverty lines differ by PPP version
poverty_lines_2021 <- c("3.0", "4.2", "8.3")
poverty_lines_2017 <- c("2.15", "3.65", "6.85")
```

# {.sidebar width="380px"}

## Data & Method Selection

### PPP Version
```{r}
shiny::radioButtons(
  "ppp_version",
  label = "PPP Version:",
  choices = c("2021" = "2021", "2017" = "2017"),
  selected = "2021"
)
```

### Significance Method
```{r}
shiny::selectInput(
  "method",
  label = "Change Detection Method:",
  choices = c(
    "Relative + Absolute Floor" = "relative",
    "Z-Score" = "zscore",
    "Absolute Difference" = "absolute"
  ),
  selected = "relative"
)
```

### Threshold
```{r}
shiny::sliderInput(
  "threshold",
  label = "Threshold:",
  min = 0,
  max = 10,
  value = 5,
  step = 0.1
)
```

### Absolute Floor (for Relative method)
```{r}
shiny::uiOutput("abs_floor_ui")
```

### Primary Indicators
```{r}
shiny::selectInput(
  "indicator",
  label = "Indicator:",
  choices = c("headcount", "mean"),
  selected = "headcount"
)
```

### Poverty Line
```{r}
shiny::selectInput(
  "poverty_line",
  label = "Poverty Line:",
  choices = poverty_lines_2021,
  selected = poverty_lines_2021[1L]
)
```

---

```{r}
#| context: server
#| label: server-core

# --- Core Reactives ---

# Reactive: current PPP dataset (full list)
merged_data <- reactive({
  if (input$ppp_version == "2021") {
    ppp_data_2021
  } else {
    ppp_data_2017
  }
})

# Reactive: threshold value (normalized to 0-1 scale for methods)
threshold_val <- reactive({
  switch(
    input$method,
    "relative" = input$threshold / 100,
    "zscore" = input$threshold,
    "absolute" = input$threshold / 100
  )
})

# Reactive: abs_floor (only used for relative method)
abs_floor_val <- reactive({
  if (input$method == "relative") {
    if (is.null(input$abs_floor)) 0.005 else input$abs_floor
  } else {
    0.005 # ignored for absolute/zscore methods
  }
})

# Reactive: human-readable label for the selected significance method
method_label <- reactive({
  switch(
    input$method,
    "relative" = "Relative + Abs. Floor",
    "zscore" = "Z-Score",
    "absolute" = "Absolute Difference",
    input$method
  )
})

# Reactive: dynamic year range bounds computed from actual data
year_range_bounds <- reactive({
  data <- merged_data()
  all_years <- c(
    data$agg_merged$reporting_year,
    data$lineups_merged$reporting_year
  )
  list(
    min = min(all_years, na.rm = TRUE),
    max = max(all_years, na.rm = TRUE)
  )
})

# Reactive: region-filtered aggregate data (shared across Aggregates page)
agg_region_filtered <- reactive({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)
  dt <- data$agg_merged[poverty_line == .pl]
  if (!is.null(input$year_range_agg)) {
    dt <- dt[
      reporting_year >= input$year_range_agg[[1L]] &
        reporting_year <= input$year_range_agg[[2L]]
    ]
  }
  if (!is.null(input$region_filter) && input$region_filter != "All") {
    dt <- dt[region_code == input$region_filter]
  }
  dt
})

# --- Dynamic UI outputs ---

# Update poverty line choices when PPP version changes
observeEvent(input$ppp_version, {
  pls <- if (input$ppp_version == "2021") {
    poverty_lines_2021
  } else {
    poverty_lines_2017
  }
  shiny::updateSelectInput(
    session,
    "poverty_line",
    choices = pls,
    selected = pls[1L]
  )
})

# Absolute floor slider (conditional on method)
output$abs_floor_ui <- shiny::renderUI({
  if (input$method == "relative") {
    shiny::sliderInput(
      "abs_floor",
      label = "Absolute Floor:",
      min = 0,
      max = 0.05,
      value = 0.005,
      step = 0.0001
    )
  }
})

# Year range sliders — bounds computed dynamically from actual data
output$year_range_agg_ui <- shiny::renderUI({
  bounds <- year_range_bounds()
  shiny::sliderInput(
    "year_range_agg",
    label = "Year Range:",
    min = bounds$min,
    max = bounds$max,
    value = c(bounds$min, bounds$max),
    step = 1L
  )
})

output$year_range_country_ui <- shiny::renderUI({
  bounds <- year_range_bounds()
  shiny::sliderInput(
    "year_range_country",
    label = "Year Range:",
    min = bounds$min,
    max = bounds$max,
    value = c(bounds$min, bounds$max),
    step = 1L
  )
})

# Country selector (populated from merged data)
country_choices <- reactive({
  data <- merged_data()
  sort(unique(data$lineups_merged$country_code))
})

output$country_selector_ui <- shiny::renderUI({
  shiny::selectInput(
    "country_filter",
    label = "Country:",
    choices = country_choices(),
    selected = country_choices()[1]
  )
})

# --- Value boxes ---

output$flagged_agg <- shiny::renderUI({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  agg_data <- data$agg_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(agg_data),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  count <- sum(flagged[[paste0(input$indicator, "_flagged")]], na.rm = TRUE)
  total <- nrow(flagged)

  bslib::value_box(
    title = "Aggregates Flagged",
    value = count,
    subtitle = paste0("out of ", total),
    theme = if (count > 0) "warning" else "success",
    showcase = bsicons::bs_icon("exclamation-triangle")
  )
})

output$flagged_lineup <- shiny::renderUI({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  lineup_data <- data$lineups_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(lineup_data),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  count <- sum(flagged[[paste0(input$indicator, "_flagged")]], na.rm = TRUE)
  total <- nrow(flagged)

  bslib::value_box(
    title = "Lineup Flagged",
    value = count,
    subtitle = paste0("out of ", total),
    theme = if (count > 0) "warning" else "success",
    showcase = bsicons::bs_icon("exclamation-triangle")
  )
})

output$flagged_survey <- shiny::renderUI({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  survey_data <- data$surveys_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(survey_data),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  count <- sum(flagged[[paste0(input$indicator, "_flagged")]], na.rm = TRUE)
  total <- nrow(flagged)

  bslib::value_box(
    title = "Survey Flagged",
    value = count,
    subtitle = paste0("out of ", total),
    theme = if (count > 0) "warning" else "success",
    showcase = bsicons::bs_icon("exclamation-triangle")
  )
})

# ---- Tabular and plot outputs ----------------------------------------

# --- Change Overview: Heatmaps (one per data source) ---

# Helper: build a plotly heatmap from flagged data
build_plotly_heatmap <- function(
  dt,
  x_col,
  y_col,
  z_col,
  title,
  method_label = ""
) {
  if (nrow(dt) == 0L) {
    return(
      plotly::plot_ly() |>
        plotly::layout(
          title = title,
          annotations = list(
            list(
              text = "No flagged data",
              x = 0.5,
              y = 0.5,
              showarrow = FALSE,
              xref = "paper",
              yref = "paper"
            )
          )
        )
    )
  }
  plotly::plot_ly(
    data = dt,
    x = dt[[x_col]],
    y = dt[[y_col]],
    z = dt[[z_col]],
    type = "heatmap",
    colorscale = list(
      list(0, "#FFFFFF"),
      list(0.5, "#FDAE61"),
      list(1, "#D73027")
    ),
    hoverinfo = "text",
    text = paste0(
      dt[[y_col]],
      " | ",
      dt[[x_col]],
      "<br>Diff: ",
      round(dt[[z_col]], 4),
      "<br>Method: ",
      method_label
    )
  ) |>
    plotly::layout(
      title = title,
      xaxis = list(title = x_col, type = "category"),
      yaxis = list(title = y_col, type = "category"),
      margin = list(l = 100)
    )
}

# Aggregates Heatmap (flagged only)
output$heatmap_agg <- plotly::renderPlotly({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)
  dt <- build_overview_agg(
    data$agg_merged,
    indicator = input$indicator,
    poverty_line = .pl,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )
  dt_flagged <- dt[flagged == TRUE]
  diff_col <- paste0(input$indicator, "_diff")
  build_plotly_heatmap(
    dt_flagged,
    x_col = "reporting_year",
    y_col = "region_code",
    z_col = diff_col,
    title = paste0("Aggregates — Flagged ", input$indicator, " Changes"),
    method_label = method_label()
  )
})

# Lineup Heatmap (flagged only)
output$heatmap_lineup <- plotly::renderPlotly({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  lineup_subset <- data$lineups_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(lineup_subset),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  flag_col <- paste0(input$indicator, "_flagged")
  diff_col <- paste0(input$indicator, "_diff")

  dt_flagged <- flagged[
    get(flag_col) == TRUE,
    .(
      country_code,
      region_code = region_code.x,
      reporting_year,
      diff = get(diff_col)
    )
  ]

  build_plotly_heatmap(
    dt_flagged,
    x_col = "reporting_year",
    y_col = "country_code",
    z_col = "diff",
    title = paste0("Lineups — Flagged ", input$indicator, " Changes"),
    method_label = method_label()
  )
})

# Survey Heatmap (flagged only)
output$heatmap_survey <- plotly::renderPlotly({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  survey_subset <- data$surveys_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(survey_subset),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  flag_col <- paste0(input$indicator, "_flagged")
  diff_col <- paste0(input$indicator, "_diff")

  dt_flagged <- flagged[
    get(flag_col) == TRUE,
    .(
      country_code,
      reporting_year,
      diff = get(diff_col)
    )
  ]

  build_plotly_heatmap(
    dt_flagged,
    x_col = "reporting_year",
    y_col = "country_code",
    z_col = "diff",
    title = paste0("Surveys — Flagged ", input$indicator, " Changes"),
    method_label = method_label()
  )
})

# Change Overview: Flagged Lineup Changes (DT with filters)
output$tbl_flagged_lineups <- DT::renderDT({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  lineup_subset <- data$lineups_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(lineup_subset),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  flag_col_name <- paste0(input$indicator, "_flagged")
  ind_x <- paste0(input$indicator, ".x")
  ind_y <- paste0(input$indicator, ".y")
  ind_diff <- paste0(input$indicator, "_diff")

  result <- flagged[, .(
    country_code,
    region_code = region_code.x,
    reporting_year,
    old_value = get(ind_y),
    new_value = get(ind_x),
    difference = get(ind_diff),
    flagged = get(flag_col_name)
  )]
  result[, .sort_key := abs(difference)]
  data.table::setorder(result, -.sort_key)
  result[, .sort_key := NULL]

  DT::datatable(
    result,
    filter = "top",
    rownames = FALSE,
    options = list(
      pageLength = 25L,
      # Default filter: flagged == TRUE (7th column, index 6)
      searchCols = list(
        NULL,
        NULL,
        NULL,
        NULL,
        NULL,
        NULL,
        list(search = "true")
      )
    )
  )
})

# Change Overview: Flagged Aggregate Changes (DT with filters)
output$tbl_flagged_agg <- DT::renderDT({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  agg_data <- data$agg_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(agg_data),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  flag_col_name <- paste0(input$indicator, "_flagged")
  ind_x <- paste0(input$indicator, ".x")
  ind_y <- paste0(input$indicator, ".y")
  ind_diff <- paste0(input$indicator, "_diff")

  result <- flagged[, .(
    region_code,
    reporting_year,
    old_value = get(ind_y),
    new_value = get(ind_x),
    difference = get(ind_diff),
    flagged = get(flag_col_name)
  )]
  result[, .sort_key := abs(difference)]
  data.table::setorder(result, -.sort_key)
  result[, .sort_key := NULL]

  DT::datatable(
    result,
    filter = "top",
    rownames = FALSE,
    options = list(
      pageLength = 25L,
      searchCols = list(
        NULL,
        NULL,
        NULL,
        NULL,
        NULL,
        list(search = '["true"]')
      )
    )
  )
})

# Change Overview: Flagged Survey Changes (DT with filters)
output$tbl_flagged_surveys <- DT::renderDT({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  survey_subset <- data$surveys_merged[poverty_line == .pl]
  flagged <- add_flag_col(
    data.table::copy(survey_subset),
    input$indicator,
    method = input$method,
    threshold = threshold_val(),
    abs_floor = abs_floor_val()
  )

  flag_col_name <- paste0(input$indicator, "_flagged")
  ind_x <- paste0(input$indicator, ".x")
  ind_y <- paste0(input$indicator, ".y")
  ind_diff <- paste0(input$indicator, "_diff")

  result <- flagged[, .(
    country_code,
    reporting_year,
    survey_year,
    old_value = get(ind_y),
    new_value = get(ind_x),
    difference = get(ind_diff),
    flagged = get(flag_col_name)
  )]
  result[, .sort_key := abs(difference)]
  data.table::setorder(result, -.sort_key)
  result[, .sort_key := NULL]

  DT::datatable(
    result,
    filter = "top",
    rownames = FALSE,
    options = list(
      pageLength = 25L,
      searchCols = list(
        NULL,
        NULL,
        NULL,
        NULL,
        NULL,
        NULL,
        list(search = "true")
      )
    )
  )
})

# Aggregates: Time Series — dynamic height container
output$plot_agg_ts_container <- shiny::renderUI({
  agg_data <- agg_region_filtered()
  n_regions <- max(1L, length(unique(agg_data$region_code)))
  h <- 400 * n_regions
  plotly::plotlyOutput("plot_agg_ts", height = paste0(h, "px"))
})

# Aggregates: Time Series (plotly)
output$plot_agg_ts <- plotly::renderPlotly({
  agg_data <- agg_region_filtered()

  if (nrow(agg_data) == 0L) {
    return(
      plotly::plot_ly() |>
        plotly::layout(
          annotations = list(list(
            text = "No data for selection",
            x = 0.5,
            y = 0.5,
            showarrow = FALSE,
            xref = "paper",
            yref = "paper"
          ))
        )
    )
  }

  ind_x <- paste0(input$indicator, ".x")
  ind_y <- paste0(input$indicator, ".y")
  n_regions <- length(unique(agg_data$region_code))
  chart_height <- max(400, 400 * n_regions)

  p <- ggplot2::ggplot(agg_data, ggplot2::aes(x = reporting_year)) +
    ggplot2::geom_line(
      ggplot2::aes(y = .data[[ind_x]], color = "New"),
      linewidth = 1
    ) +
    ggplot2::geom_line(
      ggplot2::aes(y = .data[[ind_y]], color = "Old"),
      linewidth = 1,
      linetype = "dashed"
    ) +
    ggplot2::facet_wrap(~region_code, ncol = 1, scales = "free_y") +
    ggplot2::scale_color_manual(
      values = c("New" = "#2E86AB", "Old" = "#A23B72")
    ) +
    ggplot2::labs(
      title = paste0(input$indicator, " Over Time"),
      x = "Year",
      y = input$indicator,
      color = "Version"
    ) +
    ggplot2::theme_minimal() +
    ggplot2::theme(
      legend.position = "top",
      panel.spacing = ggplot2::unit(1, "lines")
    )

  plotly::ggplotly(p, height = chart_height, tooltip = c("x", "y")) |>
    plotly::layout(legend = list(orientation = "h", y = 1.02))
})

# Aggregates: Driver Table (DT)
output$tbl_driver <- DT::renderDT({
  shiny::req(input$poverty_line, input$region_filter)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)
  .region <- input$region_filter

  .yr_max <- if (!is.null(input$year_range_agg)) {
    input$year_range_agg[[2L]]
  } else {
    max(
      data$lineups_merged[poverty_line == .pl]$reporting_year,
      na.rm = TRUE
    )
  }

  region_col <- if ("region_code.x" %in% names(data$lineups_merged)) {
    "region_code.x"
  } else {
    "region_code"
  }

  # When All/WLD, include all countries; otherwise filter by region
  if (.region %in% c("All", "WLD")) {
    lm_sub <- data$lineups_merged[
      reporting_year == .yr_max & poverty_line == .pl
    ]
  } else {
    lm_sub <- data$lineups_merged[
      get(region_col) == .region &
        reporting_year == .yr_max &
        poverty_line == .pl
    ]
  }

  name_col <- if ("country_name.x" %in% names(lm_sub)) {
    "country_name.x"
  } else {
    "country_name"
  }
  ind_x <- paste0(input$indicator, ".x")
  ind_y <- paste0(input$indicator, ".y")
  ind_diff <- paste0(input$indicator, "_diff")

  dt <- lm_sub[
    !is.na(country_code),
    .(
      country_code,
      country_name = get(name_col),
      reporting_year,
      new_val = get(ind_x),
      old_val = get(ind_y),
      indicator_diff = get(ind_diff),
      reporting_pop = reporting_pop.x
    )
  ]

  if (nrow(dt) == 0L) {
    return(DT::datatable(
      data.table(Message = "No data for selected region/year"),
      rownames = FALSE
    ))
  }

  total_pop <- sum(dt$reporting_pop, na.rm = TRUE)
  if (total_pop == 0 || is.na(total_pop)) {
    return(DT::datatable(
      data.table(Message = "No population data available"),
      rownames = FALSE
    ))
  }

  dt[, `:=`(
    pop_weight = reporting_pop / total_pop,
    weighted_contribution = indicator_diff * (reporting_pop / total_pop)
  )]
  data.table::setnames(
    dt,
    c("new_val", "old_val", "indicator_diff"),
    c(
      paste0(input$indicator, "_new"),
      paste0(input$indicator, "_old"),
      paste0(input$indicator, "_diff")
    )
  )
  dt <- dt[order(-abs(weighted_contribution))]

  DT::datatable(
    dt,
    rownames = FALSE,
    options = list(pageLength = 15L, scrollX = TRUE)
  )
})

# Aggregates: Regional Comparison Bar Chart (plotly)
output$plot_agg_bars <- plotly::renderPlotly({
  shiny::req(input$poverty_line)
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  agg_data <- data$agg_merged[poverty_line == .pl]

  # Use year_range_agg if available
  if (!is.null(input$year_range_agg)) {
    latest_year <- input$year_range_agg[[2L]]
  } else {
    latest_year <- max(agg_data$reporting_year, na.rm = TRUE)
  }
  agg_latest <- agg_data[reporting_year == latest_year]

  if (nrow(agg_latest) == 0L) {
    return(
      plotly::plot_ly() |>
        plotly::layout(
          annotations = list(list(
            text = "No data for selection",
            x = 0.5,
            y = 0.5,
            showarrow = FALSE,
            xref = "paper",
            yref = "paper"
          ))
        )
    )
  }

  ind_x <- paste0(input$indicator, ".x")
  ind_y <- paste0(input$indicator, ".y")
  agg_latest <- data.table::copy(agg_latest)
  agg_latest[, change_val := get(ind_x) - get(ind_y)]

  p <- ggplot2::ggplot(
    agg_latest,
    ggplot2::aes(x = reorder(region_code, -abs(change_val)), y = change_val)
  ) +
    ggplot2::geom_col(ggplot2::aes(fill = change_val > 0), width = 0.7) +
    ggplot2::scale_fill_manual(
      values = c("TRUE" = "#06A77D", "FALSE" = "#D62828"),
      labels = c("TRUE" = "Increase", "FALSE" = "Decrease")
    ) +
    ggplot2::coord_flip() +
    ggplot2::labs(
      title = paste0(
        input$indicator,
        " Change by Region (",
        latest_year,
        ")"
      ),
      x = "Region",
      y = paste0("Change in ", input$indicator),
      fill = "Direction"
    ) +
    ggplot2::theme_minimal() +
    ggplot2::theme(legend.position = "top")

  plotly::ggplotly(p)
})

# Country: Lineup Time Series (plotly)
output$plot_country_ts <- plotly::renderPlotly({
  shiny::req(
    input$poverty_line,
    input$country_filter,
    input$year_range_country
  )
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  lineup_data <- data$lineups_merged[
    country_code == input$country_filter &
      poverty_line == .pl &
      reporting_year >= input$year_range_country[1] &
      reporting_year <= input$year_range_country[2]
  ]

  if (nrow(lineup_data) == 0) {
    return(
      plotly::plot_ly() |>
        plotly::layout(
          annotations = list(list(
            text = "No data available",
            x = 0.5,
            y = 0.5,
            showarrow = FALSE,
            xref = "paper",
            yref = "paper"
          ))
        )
    )
  }

  ind_x <- paste0(input$indicator, ".x")
  ind_y <- paste0(input$indicator, ".y")

  plot_data <- lineup_data[, list(
    reporting_year,
    new_val = get(ind_x),
    old_val = get(ind_y)
  )]
  plot_data <- data.table::melt(
    plot_data,
    id.vars = "reporting_year",
    variable.name = "version",
    value.name = "value"
  )
  plot_data[, version := fifelse(version == "new_val", "New", "Old")]

  p <- ggplot2::ggplot(
    plot_data,
    ggplot2::aes(
      x = reporting_year,
      y = value,
      color = version,
      linetype = version
    )
  ) +
    ggplot2::geom_line(linewidth = 1) +
    ggplot2::geom_point(size = 2) +
    ggplot2::scale_color_manual(
      values = c("New" = "#2E86AB", "Old" = "#A23B72")
    ) +
    ggplot2::scale_linetype_manual(
      values = c("New" = "solid", "Old" = "dashed")
    ) +
    ggplot2::labs(
      title = paste0(input$indicator, " \u2014 ", input$country_filter),
      x = "Year",
      y = input$indicator,
      color = "Version",
      linetype = "Version"
    ) +
    ggplot2::theme_minimal() +
    ggplot2::theme(legend.position = "top")

  plotly::ggplotly(p, tooltip = c("x", "y"))
})

# Country: Survey Data Comparison (DT)
output$tbl_survey <- DT::renderDT({
  shiny::req(
    input$poverty_line,
    input$country_filter,
    input$year_range_country
  )
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  survey_data <- data$surveys_merged[
    country_code == input$country_filter &
      poverty_line == .pl &
      reporting_year >= input$year_range_country[1] &
      reporting_year <= input$year_range_country[2]
  ]

  if (nrow(survey_data) == 0) {
    return(
      DT::datatable(
        data.frame(Message = "No survey data available"),
        rownames = FALSE
      )
    )
  }

  ind_x <- paste0(input$indicator, ".x")
  ind_y <- paste0(input$indicator, ".y")
  ind_diff <- paste0(input$indicator, "_diff")

  result <- survey_data[, list(
    reporting_year,
    survey_year,
    old_value = get(ind_y),
    new_value = get(ind_x),
    difference = get(ind_diff)
  )]
  data.table::setorder(result, -reporting_year)

  DT::datatable(
    result,
    rownames = FALSE,
    options = list(pageLength = 15L, scrollX = TRUE)
  )
})

# Country: Source of Change (DT)
output$tbl_source <- DT::renderDT({
  shiny::req(
    input$poverty_line,
    input$country_filter,
    input$year_range_country
  )
  data <- merged_data()
  .pl <- as.numeric(input$poverty_line)

  source_tbl <- build_source_table(
    data$lineups_merged,
    country = input$country_filter,
    poverty_line = .pl,
    year_range = input$year_range_country
  )

  if (nrow(source_tbl) == 0) {
    return(
      DT::datatable(
        data.frame(Message = "No explanatory variable data"),
        rownames = FALSE
      )
    )
  }

  DT::datatable(
    source_tbl,
    rownames = FALSE,
    options = list(pageLength = 15L, scrollX = TRUE)
  )
})

# Country: Survey Coverage Changes (compact for sidebar)
output$tbl_coverage <- shiny::renderTable(
  {
    shiny::req(input$country_filter)
    data <- merged_data()

    survey_cov <- data$survey_coverage_diff[
      country_code == input$country_filter
    ]

    if (nrow(survey_cov) == 0) {
      return(data.frame(Message = "No survey coverage changes"))
    }

    survey_cov[, list(reporting_year, reporting_level, welfare_type, change)]
  },
  striped = TRUE,
  hover = TRUE,
  bordered = TRUE,
  spacing = "xs",
  width = "100%"
)
```

# Guide {orientation="columns"}

## How to Use This Dashboard {width="50%"}

This dashboard compares **new** PIP pipeline data against **old** (published)
data to identify meaningful changes in poverty estimates. Use the sidebar
controls to configure your analysis, then navigate through the tabs.

### Quick Start

1. **Choose your PPP version** (2021 or 2017) in the sidebar.
2. **Select an indicator** (headcount or mean) and a **poverty line**.
3. **Start on Change Overview** to see value boxes summarizing how many
   observations are flagged across aggregates, lineups, and surveys.
4. **Drill into heatmaps** — one for each data source (aggregates, lineups,
   surveys), already filtered to show only flagged observations.
5. **Go to Aggregates Detail** to explore time-series by region, see which
   countries drive aggregate changes, and compare regional differences.
6. **Go to Country Detail** to examine a single country's lineup time-series,
   survey data comparison, source-of-change variables, and survey coverage.

### Sidebar Controls

| Control | Description |
|---|---|
| **PPP Version** | Toggle between PPP 2021 (poverty lines: \$3.0, \$4.2, \$8.3/day) and PPP 2017 (\$2.15, \$3.65, \$6.85/day). |
| **Change Detection Method** | How changes are assessed for significance. See methods column. |
| **Threshold** | Sensitivity of the flagging. Lower = more flags. |
| **Absolute Floor** | Minimum absolute change required (Relative method only). Prevents flagging tiny values with large percentage swings. |
| **Indicator** | Primary poverty indicator to analyse (headcount or mean). |
| **Poverty Line** | International poverty line in \$/day (PPP). Updates automatically with PPP version. |

### Interpreting the Threshold Slider

The slider ranges from 0 to 10. Its meaning depends on the method:

- **Relative**: Threshold 5 = flag changes > 5% relative difference
- **Z-Score**: Threshold 2 = flag changes > 2 standard deviations
- **Absolute**: Threshold 1 = flag changes > 0.01 in absolute terms

Setting the threshold to 0 shows **all** changes (nothing is filtered).

## Methodology {width="50%"}

### Change Detection Methods

**Relative + Absolute Floor** *(default)*

A change is flagged when **both** conditions are met:

- The relative change exceeds the threshold: $\frac{|\text{new} - \text{old}|}{|\text{old}|} > \frac{\text{threshold}}{100}$
- The absolute change exceeds the floor: $|\text{new} - \text{old}| > \text{abs\_floor}$

The absolute floor prevents false positives from near-zero values (e.g., a
headcount moving from 0.001 to 0.002 is a 100% relative change but
meaningless in practice).

**Z-Score**

Computes the z-score of each change relative to the distribution of all
changes (trimmed at 1% tails). A change is flagged when $|z| > \text{threshold}$.
Useful for detecting outliers in the distribution of revisions.

**Absolute Difference**

Flags changes where $|\text{new} - \text{old}| > \frac{\text{threshold}}{100}$.
Simplest method — treats all changes the same regardless of the baseline level.

### Dashboard Pages

| Page | Purpose |
|---|---|
| **Guide** | This page. How to use the dashboard and methodology notes. |
| **Change Overview** | Entry point. Value boxes show total flagged changes at each level. Three heatmaps (one per data source) show flagged observations. A filterable table lists all lineup changes. |
| **Aggregates Detail** | Drill into regional aggregates. Time-series of old vs new, driver table showing which countries contribute most to a regional change, and a bar chart of change direction by region. |
| **Country Detail** | Select a country to see its lineup time-series, survey-year comparison, source-of-change variables, and survey coverage changes. |

### Data Sources

The dashboard compares three levels of PIP data:

- **Aggregates**: Regional and global poverty estimates (headcount, mean, etc.)
- **Lineups**: Country-year interpolated/extrapolated estimates aligned to common reference years.
- **Surveys**: Actual survey-year estimates from household surveys.

Each level is merged between new (pipeline) and old (published) data, with
differences computed for every indicator.

# Change Overview

## Row {height="180px"}

### Aggregates
```{r}
shiny::uiOutput("flagged_agg")
```

### Lineup
```{r}
shiny::uiOutput("flagged_lineup")
```

### Survey
```{r}
shiny::uiOutput("flagged_survey")
```

## Row

### {.tabset width="50%"}

#### Aggregates Heatmap
```{r}
plotly::plotlyOutput("heatmap_agg", height = "500px")
```

#### Lineups Heatmap
```{r}
plotly::plotlyOutput("heatmap_lineup", height = "500px")
```

#### Surveys Heatmap
```{r}
plotly::plotlyOutput("heatmap_survey", height = "500px")
```

### {.tabset width="50%"}

#### Aggregates Table
```{r}
DT::DTOutput("tbl_flagged_agg")
```

#### Lineups Table
```{r}
DT::DTOutput("tbl_flagged_lineups")
```

#### Surveys Table
```{r}
DT::DTOutput("tbl_flagged_surveys")
```

# Aggregates Detail {scrolling="true"}

## Row {height="100px"}

### {width="50%"}
```{r}
#| label: toolbar-aggregates-region
shiny::selectInput(
  "region_filter",
  label = "Region:",
  choices = c(
    "All",
    "AFE",
    "AFW",
    "EAS",
    "ECS",
    "LAC",
    "MNA",
    "SAR",
    "SSA",
    "WLD"
  ),
  selected = "All",
  width = "100%"
)
```

### {width="50%"}
```{r}
#| label: toolbar-aggregates-year
shiny::uiOutput("year_range_agg_ui")
```

## Row {.tabset}

### Time Series

```{r}
#| label: plot-agg-timeseries
shiny::uiOutput("plot_agg_ts_container")
```

### Regional Comparison

```{r}
plotly::plotlyOutput("plot_agg_bars", height = "500px")
```

### Driver Table

The driver table decomposes a regional aggregate change into country-level
contributions. Each country's **weighted contribution** equals its indicator
change × population share in the region. Sort by `weighted_contribution` to
find the main drivers. Positive = increase, negative = decrease.

```{r}
#| label: table-driver
DT::DTOutput("tbl_driver")
```

# Country Detail

## {.sidebar}

```{r}
#| label: sidebar-country
shiny::uiOutput("country_selector_ui")

shiny::uiOutput("year_range_country_ui")
```

---

**Survey coverage changes:**
```{r}
tableOutput("tbl_coverage")
```

---

**Survey Data Comparison:**
```{r}
DT::DTOutput("tbl_survey")
```

## Column

### Lineup Time Series

```{r}
plotly::plotlyOutput("plot_country_ts", height = "400px")
```

### Source of Change

```{r}
DT::DTOutput("tbl_source")
```
