---
title: "Lineup Checks"
output:
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: yeti
    orientation: columns
    social: menu
    vertical_layout: scroll
    source_code: embed
runtime: shiny
---


```{r global, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(RColorBrewer)
library(plotly)
library(purrr)
library(fst)
library(fastverse)
library(shiny)

source("R/utils.R")
pl <- 2.15

# Aggregates
dt_agg_old <- pipr::get_wb(povline = pl) |>
  qDT()
dt_agg_new <- load_from_repo("aggregates.fst")
dt_agg_old <- dt_agg_old |>
  frename(reporting_year = year)

# Survey years
dt_survey_old <- pipr::get_stats(povline = pl) |>
  qDT()
dt_survey_new <- load_from_repo("syears.fst")
dt_survey_old <- dt_survey_old |>
  frename(reporting_year = year)

# aggregates
dt_lineup_old <- pipr::get_stats(povline = pl,
                                 fill_gaps = TRUE) |>
  qDT()
dt_lineup_old <- dt_lineup_old |>
  frename(reporting_year = year)
dt_lineup_new <- load_from_repo("lyears.fst")


# survey data ---------------------
# Indicator names
survey_indicators    <- dt_survey_new |>
  fselect(headcount:decile10, spl, spr) |>
  colnames()


# Merging OLD and NEW data
surveys_merged <- join(x       = dt_survey_new,
                       y       = dt_survey_old,
                       on      = c("country_code",
                                   "reporting_year",
                                   "welfare_type",
                                   "poverty_line",
                                   "reporting_level"),
                       how     = "full",
                       verbose = FALSE,
                       suffix  = c(".x", ".y"),
                        column = list(".joyn", c("x", "y", "x & y")))

names_x <- paste0(survey_indicators, ".x")
names_y <- paste0(survey_indicators, ".y")

# Calculate the differences and assign them to new columns
surveys_merged[,
               (paste0(survey_indicators, "_diff")) := map2(mget(names_x), mget(names_y), `-`)]
# Percentage of old
surveys_merged[,
               (paste0(survey_indicators, "_perc")) := map2(mget(paste0(survey_indicators, "_diff")),
                                                            mget(names_y), `/`)]
# Ratio
surveys_merged[,
               (paste0(survey_indicators, "_ratio")) := map2(mget(names_x), mget(names_y), `/`)]

# Groups (reporting_level)
surveys_merged[, 
               unique_econ := paste0(country_code, reporting_level, welfare_type)]

# Line up year -------------
# Indicator names
lineup_indicators    <- dt_lineup_new |>
  fselect(headcount:decile10, spl, spr) |>
  colnames()


# Merging OLD and NEW data
lineups_merged <- join(x       = dt_lineup_new,
                       y       = dt_lineup_old,
                       on      = c("country_code",
                                   "reporting_year",
                                   "welfare_type",
                                   "poverty_line",
                                   "reporting_level"),
                       how     = "full",
                       verbose = FALSE,
                       suffix  = c(".x", ".y"),
                       column  = list(".joyn", c("x", "y", "x & y")) )


names_x <- paste0(lineup_indicators, ".x")
names_y <- paste0(lineup_indicators, ".y")

# if zero, reassign to being very small
lineups_merged[,
               (paste0(names_x)) := lapply(.SD,
                                           function(x) {
                                             pmax(x, 0.000001)
                                           }),
               .SDcols = names_x]
lineups_merged[,
               (paste0(names_y)) := lapply(.SD,
                                           function(x) {
                                             pmax(x, 0.000001)
                                           }),
               .SDcols = names_y]


# Calculate the differences and assign them to new columns
lineups_merged[,
               (paste0(lineup_indicators, "_diff")) :=
                 map2(mget(names_x), mget(names_y), `-`)]
# Percentage of old
lineups_merged[,
               (paste0(lineup_indicators, "_perc")) :=
                 map2(mget(paste0(lineup_indicators, "_diff")),
                      mget(names_y), `/`)]
# Ratio
lineups_merged[,
               (paste0(lineup_indicators, "_ratio")) := map2(mget(names_x), mget(names_y), `/`)]


# Outlier
amnt <- 2 # SD
lineups_merged[,
               (paste0(lineup_indicators, "_thresh_low")) :=
                 lapply(.SD,
                        function(x) {
                          mn <- mean(x, na.rm = T, trim = 0.01)
                          s  <-
                            sd(x[x > quantile(x,
                                              0.01,
                                              na.rm = T) &
                                   x < quantile(x,
                                                0.99,
                                                na.rm = T)],
                               na.rm = T)
                          mn - amnt * s
                        }),
               .SDcols = paste0(lineup_indicators, "_ratio")]

lineups_merged[,
               (paste0(lineup_indicators, "_thresh_high")) :=
                 lapply(.SD,
                        function(x) {
                          mn <- mean(x, na.rm = T, trim = 0.01)
                          s  <-
                            sd(x[x > quantile(x,
                                              0.01,
                                              na.rm = T) &
                                   x < quantile(x,
                                                0.99,
                                                na.rm = T)],
                               na.rm = T)
                          mn + amnt * s
                        }),
               .SDcols = paste0(lineup_indicators, "_ratio")]
# Groups (reporting_level)
lineups_merged[,
               unique_econ := paste0(country_code, reporting_level, welfare_type)]
# general objects
countries_available <- surveys_merged$country_code |> 
  funique()
dup_countries <- surveys_merged[, 
                                .N, 
                                by = c("country_code", 
                                       "reporting_year")][N > 1, ]$country_code |> 
  funique()

# un_econ_available <- surveys_merged |> 
#   fmutate(unique_econ = paste0(country_code, "_", reporting_level, "_", welfare_type)) |> 
#   fselect(unique_econ) |> 
#   funique()
```


Trends: Old vs New
===========================================================



Column {.sidebar}
-----------------------------------------------------------------------
```{r sidebar-plot-trends-123}
# Select Indicator
selectInput("trends_indicator", 
            label = "Compare indicator",
            choices = survey_indicators,
            selected = "mean")


# Select countries
selectInput("trend_country",
            label = "Economies",
            choices = countries_available,
            selected = "ARE",
            multiple = FALSE)
```

```{r trends-reactive}
ind <- reactive({
  input$trends_indicator
})
# country 
ct <- reactive({
  input$trend_country
})
# reactive table for trends
ST <- reactive({
  surveys_merged[country_code == ct()
                 ][, 
                   `:=`(
                       yx = get(paste0(ind(), ".x")),
                       yy = get(paste0(ind(), ".y"))
                     ) ][, 
                         text :=  paste0(
                        "Economy: ", country_code, "\n",
                        "Region: ", region_name.x, "\n",
                        "Reporting level: ", reporting_level, "\n",
                        "Welfare type: ", welfare_type, "\n",
                        "New Value:", round(yx, 4), "\n",
                        "Old Value:", round(yy, 4), "\n",
                        "Year: ", reporting_year)
                        ] 
})

LT <- reactive({
  lineups_merged[country_code == ct()
                 ][, 
                   `:=`(
                       yx = get(paste0(ind(), ".x")),
                       yy = get(paste0(ind(), ".y"))
                     ) ][, 
                         text :=  paste0(
                        "Economy: ", country_code, "\n",
                        "Region: ", region_name.x, "\n",
                        "Reporting level: ", reporting_level, "\n",
                        "Welfare type: ", welfare_type, "\n",
                        "New Value:", round(yx, 4), "\n",
                        "Old Value:", round(yy, 4), "\n",
                        "Year: ", reporting_year)
                        ] 
})
```

Column
-----------------------------------------------------------------------

### Survey Years

```{r trends-svy}
renderPlotly({

  g_trends(dt = ST(), country = ct(), indicator = ind())

})
```

Column
-----------------------------------------------------------------------

### Lineups

```{r trends-lny}
renderPlotly({
  
  g_trends(dt = LT(), country = ct(), indicator = ind())
  
})
```


Survey years
===========================================================


Column {.sidebar}
-----------------------------------------------------------------------
```{r sidebar-plot-survey-3}
# Select Indicator
selectInput("survey_indicator",
            label = "Compare indicator:",
            choices = survey_indicators,
            selected = "mean")

# Select countries
selectInput("survey_country",
            label = "Economies:",
            choices = c("All", countries_available),
            selected = "All",
            multiple = TRUE)


# Select countries
selectInput("survey_percentage",
            label = "Percentage (i.t.o old) or real difference:",
            choices = c("Percentage change", "Real difference", "Ratio"),
            selected = "Percentage change",
            multiple = FALSE)


# Select countries
sliderInput(
  "survey_outlier",
  label = "Outlier detection - sd threshold",
  value = 2,
  min   = 0,
  max   = 3.5,
  step = 0.1
)

selectInput(
  "survey_outlier_yes",
  label = "Is outlier",
  choices = c("Yes", "No"),
  selected = "Yes",
  multiple = FALSE
)

```

```{r survey-data-reactive}
svy_ind <- reactive({
  input$survey_indicator
})

svy_ct <- reactive({
  input$survey_country
})

svy_chg <- reactive({
  input$survey_percentage
})

survey_indicator <- reactive({

  # Copy data table
  survey_indicator <- copy(surveys_merged)
  
  if (!svy_chg() == "Ratio") {
    if (svy_chg() == "Percentage change") {
      # indicator
      setnames(survey_indicator,
               old = (paste0(svy_ind(), "_perc")),
               new = "New_minus_old")
      
    } else {
      # indicator
      setnames(survey_indicator,
               old = (paste0(svy_ind(), "_diff")),
               new = "New_minus_old")
    }
  } else {
    setnames(survey_indicator,
             old = (paste0(svy_ind(), "_ratio")),
             new = "New_minus_old")
  }
  
  if (!"All" %chin% svy_ct()) {
    survey_indicator <- survey_indicator |>
      fsubset(country_code %in% svy_ct())
  }
  
  # Tooltip
  survey_indicator[,
                   text_tooltip :=
                     paste0(
                       "Economy: ", country_code,"\n",
                       "Region: ", region_name.x, "\n",
                        "Reporting level: ", reporting_level, "\n",
                       "Value: ", round(New_minus_old, 4),"\n",
                       "Year: ", reporting_year
                     )]
  
  survey_indicator
  
})

survey_baltman <- reactive({
  # Copy data table
  survey_indicator <- surveys_merged
  ind <- paste(input$survey_indicator)
  
  if (!"All" %chin% input$survey_country) {
    survey_indicator <- survey_indicator |>
      fsubset(country_code %in% input$survey_country)
  }
  survey_indicator[,
                   `:=`(diff = get(paste0(ind, ".x")) -
                          get(paste0(ind, ".y")),
                        mean_btw = (get(paste0(ind, ".x")) +
                                      get(paste0(ind, ".y"))) / 2)]
  # Tooltip
  survey_indicator[,
                   text_tooltip :=
                     paste0(
                       "Economy: ", country_code,"\n",
                       "Region: ", region_name.x, "\n",
                       "Reporting level: ", reporting_level, "\n",
                       "Mean old and new: ",round(mean_btw, 4),"\n",
                       "Difference: ",round(diff, 4),"\n",
                       "Year: ",reporting_year
                     )]
  survey_indicator
  
})

survey_outlier <- reactive({
  
  # Copy data table
  survey_indicator <- copy(surveys_merged)
  
  
  # Define low and high thresholds
  survey_indicator <- survey_indicator |> 
    fmutate(New = get(paste0(svy_ind(), ".x")),
            Old = get(paste0(svy_ind(), ".y")),
            new_old =  abs(New - Old) / Old ) 
    # survey_indicator[, new_old := 
    #                abs(get(svy_ind(), ".x") - get(svy_ind(), ".y")) /
    #                  get(svy_ind(), ".y")]
  survey_indicator[,
                 `:=`(
                   thres_new_old_lo = mean(new_old, na.rm = TRUE) -
                     input$survey_outlier * sd(new_old, na.rm = TRUE),
                   thres_new_old_hi = mean(new_old, na.rm = TRUE) +
                     input$survey_outlier * sd(new_old, na.rm = TRUE)
                 )]
  
  # Inside or outside threshold
  survey_indicator <- 
    if (input$survey_outlier_yes == "Yes") {
    survey_indicator[!between(new_old, thres_new_old_lo, thres_new_old_hi)]
  } else {
    survey_indicator[between(new_old, thres_new_old_lo, thres_new_old_hi)]
  }
  
  survey_indicator <- survey_indicator |>
    fselect("country_code",
            "reporting_year",
            "welfare_type",
            "Old",
            "New")
  
  setnames(survey_indicator,
           old = c("Old", "New"),
           new = c(paste0(c("Old_", "New_"), svy_ind())))
  
  survey_indicator
  
  
})

```


Column {.tabset data-width=600} 
-----------------------------------------------------------------------

### Difference over time 


```{r plot-survey}
renderPlotly({
   
  g <- ggplot(data = survey_indicator(), 
              aes(x      = reporting_year,
                  y      = New_minus_old,
                  colour = region_code.x,
                  group  = unique_econ)) +
          geom_point(aes(text = text_tooltip)) +
          geom_line() +
    theme_classic() +
    scale_color_brewer(palette = "Dark2") +
    labs(title = "New Vs old",
         x     = "Reporting Year",
         y     = paste0("Difference in ",
                        svy_ind(),
                        ifelse(grepl("[Pp]ercentage", input$survey_percentage), 
                               " %", ""),
                        " (new minus old)"))

  g <- ggplotly(g, tooltip = "text")

  g

})

```

### Scatterplot of old vs new estimates

```{r}
renderPlotly({
  

  g <- ggplot(data = survey_indicator(),
              aes(x = get(paste0(svy_ind(), ".y")),
                  y = get(paste0(svy_ind(), ".x")),
                  color = region_code.x,
                  group = unique_econ)) +
    geom_point(aes(text = text_tooltip)) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.3) +
    theme_classic() +
    scale_color_brewer(palette = "Dark2") +
    labs(title = "Scatter plot new survey estimate minus old",
         x     = paste("Old", svy_ind()),
         y     = paste("New", svy_ind()))

  g <- ggplotly(g, tooltip = "text")

  g
})
```


### Bland-Altman plot

```{r}
renderPlotly({


  g <- ggplot(data = survey_baltman(),
              aes(x = mean_btw,
                  y = diff,
                  color = region_code.x)) +
        geom_point(aes(text = text_tooltip)) +
    theme_classic() +
    scale_color_brewer(palette = "Dark2") +
    labs(title = "Bland-Altman Plot",
         x     = paste("Mean of old and new", svy_ind()),
         y     = paste("Difference between old and new", svy_ind()))

  g <- ggplotly(g, tooltip = "text")

  g
})
```



Column {data-width=400}
-----------------------------------------------------------------------

### Table of outliers


```{r}
renderTable({
  survey_outlier()
})

```





Lineup years
===========================================================


Column {.sidebar}
-----------------------------------------------------------------------
```{r sidebar-plot-lineup-3}
# Select Indicator
selectInput("lineup_indicator",
            label = "Compare indicator:",
            choices = lineup_indicators,
            selected = "mean")

# Select countries
selectInput("lineup_country",
            label = "Economies:",
            choices = c("All", countries_available),
            selected = "All",
            multiple = TRUE)


# Select countries
selectInput("lineup_percentage",
            label = "Percentage (i.t.o old) or real difference:",
            choices = c("Percentage change", "Real difference", "Ratio"),
            selected = "Percentage change",
            multiple = FALSE)


# Select countries
sliderInput(
  "lineup_outlier",
  label = "Outlier detection - sd threshold",
  value = 2,
  min   = 0,
  max   = 3.5,
  step = 0.1
)

selectInput(
  "lineup_outlier_yes",
  label = "Is outlier",
  choices = c("Yes", "No"),
  selected = "Yes",
  multiple = FALSE
)

```

```{r lineup-data-reactive}
lineup_ind <- reactive({
  input$lineup_indicator
})

lineup_ct <- reactive({
  input$lineup_country
})

lineup_chg <- reactive({
  input$lineup_percentage
})

lineup_indicator <- reactive({

  # Copy data table
  lineup_indicator <- copy(lineups_merged)
  
  if (!lineup_chg() == "Ratio") {
    if (lineup_chg() == "Percentage change") {
      # indicator
      setnames(lineup_indicator,
               old = (paste0(lineup_ind(), "_perc")),
               new = "New_minus_old")
      
    } else {
      # indicator
      setnames(lineup_indicator,
               old = (paste0(lineup_ind(), "_diff")),
               new = "New_minus_old")
    }
  } else {
    setnames(lineup_indicator,
             old = (paste0(lineup_ind(), "_ratio")),
             new = "New_minus_old")
  }
  
  if (!"All" %chin% lineup_ct()) {
    lineup_indicator <- lineup_indicator |>
      fsubset(country_code %in% lineup_ct())
  }
  
  # Tooltip
  lineup_indicator[,
                   text_tooltip :=
                     paste0(
                       "Economy: ", country_code,"\n",
                       "Region: ", region_name.x, "\n",
                       "Reporting level: ", reporting_level, "\n",
                       "Value: ", round(New_minus_old, 4),"\n",
                       "Year: ", reporting_year
                     )]
  
  lineup_indicator
  
})

lineup_baltman <- reactive({
  # Copy data table
  lineup_indicator <- lineups_merged
  ind <- paste(input$lineup_indicator)
  
  if (!"All" %chin% input$lineup_country) {
    lineup_indicator <- lineup_indicator |>
      fsubset(country_code %in% input$lineup_country)
  }
  lineup_indicator[,
                   `:=`(diff = get(paste0(ind, ".x")) -
                          get(paste0(ind, ".y")),
                        mean_btw = (get(paste0(ind, ".x")) +
                                      get(paste0(ind, ".y"))) / 2)]
  # Tooltip
  lineup_indicator[,
                   text_tooltip :=
                     paste0(
                       "Economy: ", country_code,"\n",
                       "Region: ", region_name.x, "\n",
                       "Reporting level: ", reporting_level, "\n",
                       "Mean old and new: ",round(mean_btw, 4),"\n",
                       "Difference: ",round(diff, 4),"\n",
                       "Year: ",reporting_year
                     )]
  lineup_indicator
  
})

lineup_outlier <- reactive({
  
  # Copy data table
  lineup_indicator <- copy(lineups_merged)
  
  
  # Define low and high thresholds
  lineup_indicator <- lineup_indicator |> 
    fmutate(New = get(paste0(lineup_ind(), ".x")),
            Old = get(paste0(lineup_ind(), ".y")),
            new_old =  abs(New - Old) / Old ) 

    lineup_indicator[,
                 `:=`(
                   thres_new_old_lo = mean(new_old, na.rm = TRUE) -
                     input$lineup_outlier * sd(new_old, na.rm = TRUE),
                   thres_new_old_hi = mean(new_old, na.rm = TRUE) +
                     input$lineup_outlier * sd(new_old, na.rm = TRUE)
                 )]
  
  # Inside or outside threshold
  lineup_indicator <- 
    if (input$lineup_outlier_yes == "Yes") {
    lineup_indicator[!between(new_old, thres_new_old_lo, thres_new_old_hi)]
  } else {
    lineup_indicator[between(new_old, thres_new_old_lo, thres_new_old_hi)]
  }
  # Inside or outside threshold
  # lineup_indicator <- 
  #   if (input$lineup_outlier_yes == "Yes") {
  #   lineup_indicator[!between(new_old, 
  #                             get(paste0(lineup_ind(), "_thresh_low")), 
  #                             get(paste0(lineup_ind(), "_thresh_high")))]
  # } else {
  #       lineup_indicator[between(new_old, 
  #                             get(paste0(lineup_ind(), "_thresh_low")), 
  #                             get(paste0(lineup_ind(), "_thresh_high")))]
  # }
  
  lineup_indicator <- lineup_indicator |>
    fselect("country_code",
            "reporting_year",
            "welfare_type",
            "Old",
            "New")
  
  setnames(lineup_indicator,
           old = c("Old", "New"),
           new = c(paste0(c("Old_", "New_"), svy_ind())))
  
  lineup_indicator
  
  
})

```


Column {.tabset data-width=600} 
-----------------------------------------------------------------------

### Difference over time 


```{r plot-lineup}
renderPlotly({
   
  g <- ggplot(data = lineup_indicator(), 
              aes(x      = reporting_year,
                  y      = New_minus_old,
                  colour = region_code.x,
                  group  = unique_econ)) +
          geom_point(aes(text = text_tooltip)) +
          geom_line() +
    theme_classic() +
    scale_color_brewer(palette = "Dark2") +
    labs(title = "New Vs old",
         x     = "Reporting Year",
         y     = paste0("Difference in ",
                        lineup_ind(),
                        ifelse(grepl("[Pp]ercentage", input$lineup_percentage), 
                               " %", ""),
                        " (new minus old)"))

  g <- ggplotly(g, tooltip = "text")

  g

})

```

### Scatterplot of old vs new estimates

```{r}
renderPlotly({
  

  g <- ggplot(data = lineup_indicator(),
              aes(x = get(paste0(lineup_ind(), ".y")),
                  y = get(paste0(lineup_ind(), ".x")),
                  color = region_code.x,
                  group = country_code)) +
    geom_point(aes(text = text_tooltip)) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.3) +
    theme_classic() +
    scale_color_brewer(palette = "Dark2") +
    labs(title = "Scatter plot new survey estimate minus old",
         x     = paste("Old", lineup_ind()),
         y     = paste("New", lineup_ind()))

  g <- ggplotly(g, tooltip = "text")

  g
})
```


### Bland-Altman plot

```{r}
renderPlotly({


  g <- ggplot(data = lineup_baltman(),
              aes(x = mean_btw,
                  y = diff,
                  color = region_code.x)) +
        geom_point(aes(text = text_tooltip)) +
    theme_classic() +
    scale_color_brewer(palette = "Dark2") +
    labs(title = "Bland-Altman Plot",
         x     = paste("Mean of old and new", lineup_ind()),
         y     = paste("Difference between old and new", lineup_ind()))

  g <- ggplotly(g, tooltip = "text")

  g
})
```



Column {data-width=400}
-----------------------------------------------------------------------

### Table of outliers


```{r}
renderTable({
  lineup_outlier()
})

```




Compare missing data
===========================================================

```{r missing-data}
# SURVEYS-------------------------------------------
names_x_survey <- paste0(survey_indicators, ".x")
names_y_survey <- paste0(survey_indicators, ".y")

# Create a logical vector to filter rows
filter_condition_survey <- Reduce("|",
                                 lapply(seq_along(names_x_survey),
                                        function(i) {is.na(surveys_merged[[names_x_survey[i]]]) &
                                            !is.na(surveys_merged[[names_y_survey[i]]])}))

NAs_x_survey <- surveys_merged[filter_condition_survey,] |>
    fselect(country_code, reporting_year, reporting_level, welfare_type)
filter_condition_survey <- Reduce("|",
                                 lapply(seq_along(names_x_survey),
                                        function(i) {!is.na(surveys_merged[[names_x_survey[i]]]) &
                                            is.na(surveys_merged[[names_y_survey[i]]])}))

NAs_y_survey <- surveys_merged[filter_condition_survey,]  |>
    fselect(country_code, 
            reporting_year, 
            reporting_level, 
            welfare_type)

# LINEUP-------------------------------------------

names_x_lineup <- paste0(lineup_indicators, ".x")
names_y_lineup <- paste0(lineup_indicators, ".y")

# Create a logical vector to filter rows
filter_condition_lineup <- Reduce("|",
                                 lapply(seq_along(names_x_lineup),
                                        function(i) {is.na(lineups_merged[[names_x_lineup[i]]]) &
                                            !is.na(lineups_merged[[names_y_lineup[i]]])}))
NAs_x_lineup <- lineups_merged[filter_condition_lineup,] |>
    fselect(country_code, reporting_year, reporting_level, welfare_type)
filter_condition_lineup <- Reduce("|",
                                 lapply(seq_along(names_x_lineup),
                                        function(i) {!is.na(lineups_merged[[names_x_lineup[i]]]) &
                                            is.na(lineups_merged[[names_y_lineup[i]]])}))
NAs_y_lineup <- lineups_merged[filter_condition_lineup,] |>
    fselect(country_code, 
            reporting_year, 
            reporting_level, 
            welfare_type)
```



Column {data-width=1000}
-----------------------------------------------------------------------
### In Old but not New (survey)

```{r}
renderTable({
  surveys_merged |>
    fsubset(.joyn == "y") |>
    fselect(country_code, 
            reporting_year, 
            reporting_level, 
            welfare_type)
})
```

### In New but not Old (survey)

```{r}
renderTable({
  surveys_merged |>
    fsubset(.joyn == "x") |>
    fselect(country_code, 
            reporting_year, 
            reporting_level, 
            welfare_type)
})
```

### NAs in New

```{r}
renderTable({
  NAs_x_survey
})
```


### NAs in Old

```{r}
renderTable({
  NAs_y_survey
})
```


Column {data-width=1000}
-----------------------------------------------------------------------

### In Old but not New (lineup)

```{r}
renderTable({
  lineups_merged |>
    fsubset(.joyn == "y") |>
    fselect(country_code, 
            reporting_year, 
            reporting_level,
            welfare_type)
})
```

### In New but not Old (lineup)

```{r}
renderTable({
  lineups_merged |>
    fsubset(.joyn == "x") |>
    fselect(country_code, reporting_year, reporting_level, welfare_type)
})
```




### NAs in New (lineup)

```{r}
renderTable({
  NAs_x_lineup
})
```


### NAs in Old (lineup)

```{r}
renderTable({
  NAs_y_lineup
})
```


